Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-06-11 manuscript.qmd
expand appendix by two paragraphs

>>>>

The distribution that marginalizes over the unknown midline extension cases is shifted towards a lower prevalence. This makes intuitive sense: With only six patients among the 65 with unknown midline extension status, the upper bound for the prevalence has moved down compared to six out of 29.

We chose to compare our model against such corrected prevalence posteriors, because the model, too, is capable of marginalizing over unknown midline extension in the data. It would therefore be inaccurate to compare the model trained with the full dataset to only that part of the patient cohort where the tumor lateralization was recorded.
